---
title: "Interactivity in R with JS"
author: "timelyportfolio"
date: "February 24, 2015"
output:
  revealjs::revealjs_presentation:
    mathjax: null
    center: true
---

## Interactivity in R

### Wading into a pool of promise littered with "failure"


### ubiquity + innovation of web -> promise within reach


### Will limit this discussion of interactivity to R + JS/HTML

## How to Get JS -> R

- [V8](https://www.opencpu.org/posts/v8-release-0-5/)
- manually | [htmltools](https://github.com/rstudio/htmltools) | [rmarkdown](http://rmarkdown.rstudio.com)
- [**htmlwidgets**](http://htmlwidgets.org)

## How to Get R <-> JS

- manually
- [Shiny](http://shiny.rstudio.com)

## V8

> Not really interactive, but why rewrite good code?


```{r}
library(V8)

ct <- new_context( "window" )
ct$eval ( 
  " console.log( ['I am in JavaScript. 1+1 = ', 1 + 1].join('') ) "
)
```

## V8 (more powerful examples)

[geospatial analysis with Turf.js](https://gist.github.com/timelyportfolio/9b4fc699bb6d67b7f418)

[pdf creation with libharu](http://bl.ocks.org/timelyportfolio/81208f44c520419015f7)

[SQLite](https://www.opencpu.org/posts/v8-release-0-5/)



## Manually

```
<div id = "manual-example"></div>
<script>
  document.getElementById("manual-example")
    .innerText = "ugly manual example"
</script>
```
<div id = "manual-example"></div>
<script>
  document.getElementById("manual-example").innerText = "ugly manual example"
</script>


## htmlwidgets

Use JavaScript without knowing any JavaScript

```{r echo = F}
library(DiagrammeR)
mermaid("
  sequenceDiagram;
    participant R;
    Note left of R: Get Data<br/>Do Calculations
    htmlwidgets->>R: dependencies, binding 
    alt Static
      R->>Browser: json;
      Note right of Browser: User Interact
    else Shiny
      loop continuously in response to event
        R-->>Browser: json over socket;
        Browser-->>R: json over socket;
        Note left of R: Get Data<br/>Do Calculations
        Note right of Browser: User Interact
      end
    end
", height = 400, width = 600)
```

## htmlwidgets - Leaflet

```{r}
library(leaflet)
m = leaflet( width = 400, height = 400) %>% addTiles()
m %>% setView( -86.8034743, 33.5025432, zoom=17 )
```

## htmlwidgets - rpivotTable

```{r}
library(rpivotTable)

rpivotTable( data.frame(Titanic) )
```

## htmlwidgets - qtlcharts

```{r}
library(qtlcharts)
data(geneExpr)
iplotCorr( geneExpr$expr, geneExpr$genotype, reorder=TRUE
   ,chartOpts=list( height = 400, width = 800 )
)
```

---

```{r echo = F}
library(qtlcharts)
# random growth curves, based on some data
times <- 1:16
n <- 100
start <- rnorm(n, 5.2, 0.8)
slope1to5 <- rnorm(n, 2.6, 0.5)
slope5to16 <- rnorm(n, 0.24 + 0.09*slope1to5, 0.195)
y <- matrix(ncol=16, nrow=n)
y[,1] <- start
for(j in 2:5)
    y[,j] <- y[,j-1] + slope1to5
for(j in 6:16)
    y[,j] <- y[,j-1] + slope5to16
y <- y + rnorm(prod(dim(y)), 0, 0.35)


iplotCurves(y, times, y[,c(1,5)], y[,c(5,16)],
  chartOpts=list(curves_xlab="Time", curves_ylab="Size",
     scat1_xlab="Size at T=1", scat1_ylab="Size at T=5",
     scat2_xlab="Size at T=5", scat2_ylab="Size at T=16"
  )
)

```

## htmlwidgets - svgPanZoom

```{r warning = F, message=F}
library(SVGAnnotation)
library(svgPanZoom)
svgPanZoom(
  svgPlot(image(volcano), height = 400, width = 400)
  ,controlIconsEnabled = T
)
```

## htmlwidgets - epiwidgets

```{r warning = F, echo = T, eval =F}
library(epiwidgets)
library(ape)
data(bird.orders)
htmlwidgets::as.iframe(
  treewidget(bird.orders,height = 400, width = 800)
)
```

---
```{r warning = F, echo = F, eval =T}
library(epiwidgets)
library(ape)
data(bird.orders)
htmlwidgets::as.iframe(
  treewidget(bird.orders,height = 500, width = 600)
  ,libdir="lib"
  ,height = 650
)